\documentclass{article}
\usepackage{blindtext}
\usepackage[left=2.75cm, right=2.75cm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{systeme}
\title{\large{\vspace{-1.0cm}CS-2050, B1, Instructor: Sweat, Monica \\ HW3 ; Alexander Guo}}
\date{}

\begin{document}

\maketitle

\vspace{-1.5cm}

\textbf{Section 1.4}

\begin{enumerate}

\item[6.)]

\begin{enumerate}

\item[a.] There is a student in my school who has visited North Dakota.

\item[e.] It is not the case that the students in my school have visited North Dakota.

\item[f.] All students in my school have not visited North Dakota.

\end{enumerate}

\item[8.)]

\begin{enumerate}

\item[a.] For every animal, if it is a rabbit, then it hops.

\item[d.] There exists an animal such that it is a bunny and hops.

\end{enumerate}

\item[10.)]

\begin{enumerate}

\item[a.] $\exists x ( C(x) \wedge D(x) \wedge F(x) )$

\item[c.] $\exists x ( C(x) \wedge F(x) \wedge \neg D(x) )$

\item[d.] $\neg \exists x ( C(x) \wedge D(x) \wedge F(x) )$

\end{enumerate}

\item[32.)]

\begin{enumerate}

\item[a.] Let us express the predicate, F(x), as "x has fleas", in addition to D(x), which is "x is a dog", with the domain being all animals. The original statement can be written as $\forall x ( D(x) \rightarrow F(x) )$. The negation of this statement is $\neg \forall x (D(x) \rightarrow F(x) ) \equiv \exists x \neg (D(x) \rightarrow F(x))$. In english, it means there exists an animal such that it is a dog and doesn't have fleas.

\item[b.] Let us express the predicate, A(x), as "x can add", in addition to H(x), which is "x is a horse", with the domain being all animals. The original statment can be written as $\exists x ( H(x) \rightarrow A(x) )$. The negation of this statement is $\neg \exists x (H(x) \rightarrow A(x)) \equiv \forall x \neg (H(x) \rightarrow A(x))$. In english, it means for all animals, it is a horse and doesn't add. 

\end{enumerate}

\end{enumerate}

\textbf{Section 1.5}

\begin{enumerate}

\item[4.)]

\begin{enumerate}

\item[b.]

\item[e.]

\end{enumerate}

\end{enumerate}

\end{document}